---
output: html_document
title: Curriculum vitae
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<br>

------

### **Education**

<br>

**Cornell University**: Doctor of Philosophy candidate in Applied Ecology (projected finish: 2023)

* Concentrations: Fishery & Aquatic Sciences, Quantitative Ecology, and Human Dimensions to Natural Resource Management

**SUNY College of Environmental Science and Forestry**: Master of Science in Ecology (2013)

**Maxwell School of Citizenship at Syracuse University**: Master of Public Administration (2013)

**SUNY College at Brockport**: Bachelor of Science in Environmental Science and Biology (2008)

<br>

------


### **Professional Experience**

<br>

#### Cornell University (Ithaca, NY)

**Graduate Research Assistant, Applied Ecology (2019 - present)**

* Using long-term monitoring datasets to understand the lower trophic levels of the Great Lakes
* Launched a Zooplankton as Indicators ([ZIG](https://sfigary.github.io/website/ZIG.html)) project in Nov 2019 (>140 participants) as part of the Global Lake Ecological Observatory Network to investigate the use of zooplankton as indicators with a global dataset ([L&O Community News](https://aslopubs.onlinelibrary.wiley.com/doi/full/10.1002/lob.10515)). 

<br>

#### USEPA, Office of Research and Development (Narragansett, RI)

**Oak Ridge Institute of Science and Education Research Participant (2015 - 2019)**

* Determined the impact of impervious cover on macroinvertebrate communities in intermittent and perennial streams using Threshold Indicator Taxa ANalysis in R and introduced a statistical R package, pTITAN2
*	Developed a Spatial Statistical Network stream temperature model to guide the Houlton Band of Maliseet Indians riparian restoration priorities by predicting several restoration scenarios using four restored riparian buffer widths ([published](http://www.sciencedirect.com/science/article/pii/S0301479720315103))
 
<br>

#### Wissahickon Trails (former Wissahickon Valley Watershed Association, Ambler, PA)

**Water Quality Program Manager (2014 - 2015)**

*	Team leader and program manager of a $143K/year Delaware River Watershed Initiative (DRWI) grant
*	Expanded an existing water quality program by (1) improving the statistical quality of data by implementing a QA/QC plan, (2) bolstering sampling at restoration sites to quantify improvements, and (3) leading the DWRI water quality sub-committee and implementing monitoring plans, QA/QC practices, and developing a water quality database for four partner watershed organizations

**Independent Contractor (2016 - 2017)**

*	Quantified trends in habitat, macroinvertebrate, and water quality with over a decade of monitoring data
*	Summarized findings for public, municipalities, and scientific audiences in a white paper (92 pages)

<br>

#### SUNY ESF (Syracuse, NY)

**Graduate Research Assistant, Ecology (2009 - 2011)**

* Investigated invertebrate dispersal to newly created vernal pools in an experimental forest (39 ponds) and survey ponds (40 ponds) surrounding the experimental forest ([published](https://esajournals.onlinelibrary.wiley.com/doi/full/10.1002/ecs2.1377))
*	Led field sampling, analyzed water chemistry, created a database, and identified invertebrates 

**Graduate Teaching Assistant (2011 - 2012)**

* Taught upper level courses: Marine Ecology (~100 students) and Limnology (~80 students)
*	Led weekly lecture presentations on ecological concepts, organisms, and foundation water quality sampling and laboratory methods


<br>

#### Clarkson University (Potsdam, NY)

**Research Technician, Limnology (2009)**

* Determined the accuracy and precision of aquatic research equipment, the bbe FluoroProbe® ([published](https://cdnsciencepub.com/doi/abs/10.1139/cjfas-2013-0599))


<br>

#### Research Foundation (Brockport, NY)

**Research Technician, Limnology (2007 - 2008)**

* Analyzed water quality samples following Standard Operating Procedures, maintaining laboratory databases, and ensuring Quality Assurance/Quality Control practices in accordance to NELAC


<br>

------

### **Awards and Successful Grant Applications**

* USGS John Wesley Powell Center for Analysis and Synthesis funding working group titled ["Synthesizing patterns and drivers of changes in lake zooplankton community dynamics worldwide"](https://www.usgs.gov/centers/john-wesley-powell-center-for-analysis-and-synthesis/science/synthesizing-patterns-and)
* IAGLR David M. Dolan Quantitative Ecology [Scholarship](http://iaglr.org/awards-scholarships/dolan-scholarship/). 2021.
* Serve-in-Place. 2021. $700. [Vaccination Conversations with Scientists.](https://gradcareers.cornell.edu/opportunities/vaccination-conversations-with-scientists-vacs/) 
* WVWA. Growing Greener. 2015. $369,600. Stream restoration.
* WVWA. William Penn Foundation. 2015. $82,500. Stakeholder collaboration.
* WVWA. National Fish and Wildlife Foundation. 2015. $190,000. Restoration construction plans.
* SUNY ESF. Seven grants totaling $8500 for research and travel funds.

<br>

------

### **Professional Societies**

* Association for the Sciences of Limnology and Oceanography
* Ecological Society of America
* Society for Freshwater Science
* Global Lake Ecological Observatory Network
* International Association for Great Lakes Research


<br>

------

### **Certifications and Workshops**

* Colman Inclusive Leadership  [Program.](https://gradschool.cornell.edu/diversity-inclusion/signature-initiatives/colman-leadership-program/) Ithaca, N.Y.
* Communications Boot Camp for Scientists. American Institute of Biological Sciences. Washington, D.C. 
* Certified Wetland Delineator, Rutgers University 
* Open Water Dive and Dry Suit Certified
* New York Boater Safety Course


<br>

------

### **Presentations (past ten years)**

*  **Figary, S.**, J. M. Watkins, L. G. Rudstam. Jan 2023. Zooplankton indicator development for Erie, Great Lakes, and globally. Department of Natural Resources Symposium. Ithaca, New York. Presentation.

*  Bruel, R., Z. Ersoy and others including **S. Figary**. Nov 2022. ZooSize – Crustacean zooplankton community size distribution across a worldwide set of freshwater lakes. GLEON All-hands meeting. Lake George, New York. Poster.

* Jordan, P. D., **S. Figary**, C. Hotaling, A. VanDeValk, T. Brooking, L. Rudstam. Sept 2022.  Invasive Bythotrephes longimanus are selected by Age-0 Yellow Perch and do not negatively affect perch growth. PERCIS V, Biology of Percid Fishes. Ceske Budejovice, Czech Republic. Presentation.

* **Figary, S.**, K. Holeck, J. M. Watkins, L. G. Rudstam. May 2022. The nearshore habitat of large lakes may be an early indicator of future offshore changes. Joint Aquatic Sciences Meeting. Grand Rapids, Michigan. Presentation.

* Kovalenko, K., E. D. Reavie, **Figary, S.**, L. G. Rudstam, J. M. Watkins, C. T. Filstrup. May 2022. Zooplankton-phytoplankton relationships in the Great Lakes. Joint Aquatic Sciences Meeting. Grand Rapids, Michigan. Presentation.

* Scofield, A., J. M. Watkins, **Figary, S.**, J. E. Lietz, L. G. Rudstam. May 2022. Insights from extensive zooplankton length data from a long-term monitoring program. Joint Aquatic Sciences Meeting. Grand Rapids, Michigan. Presentation.

* **Figary, S.**, R. Barbiero, D. Kane, J. Hood, S. Ludsin, L. Rudstam, J. Watkins, and C. Winslow. March 2022. Using zooplankton to track ecosystem condition in Lake Erie. State of Lake Erie Conference. Cleveland, Ohio. Presentation. 

* Watkins, J., L. Rudstam, **S. Figary**, W. Currie, K. Bowen. March 2022. Seasonal succession of zooplankton in Lake Erie in 2019. State of Lake Erie Conference. Cleveland, Ohio. Presentation. 

*	**Figary, S.**, K. Holeck, J. Watkins, and L. Rudstam. Comparing Lake Ontario’s nearshore and offshore zooplankton communities using long term monitoring datasets. Presentation.
    + March 2021. State of Lake Ontario Conference. Virtual. 
    + May 2021. International Association for Great Lakes Research Annual Conference. **David M. Dolan Quantitative Ecology Scholarship** presentation. Virtual. 
    + September 2021. New York Department of Conservation Partner’s Meeting. Virtual. 


*	**Figary, S.**, N. Detenbeck, and C. O’Donnell. Creating a high resolution spatial statistical network model to guide riparian restoration strategies in a transboundary watershed. Presentation.
    + March 2020. Northeast Aquatic Biologists Conference. Newport, Rhode Island. **Best student presentation award.**
    + April 2020. Vermont’s Department of Environmental Conservation Watershed Division. **Invited** webinar.
    +  May 2020. Maine Stream Temperature Monitoring Working Group. **Invited** webinar.


*	**Figary, S.**. Jan 2020. Exploring variability in the Great Lakes using lower trophic levels. Department of Natural Resources Symposium. Ithaca, New York. Presentation. 

*	**Figary, S.**, L. G. Rudstam, and J. M. Watkins. Nov 2019. Determining zooplankton community response to changing water quality parameters in large lakes using Taxa Indicator Threshold ANalysis (TITAN). Global Lake Ecological Observatory Network All-Hands meeting. Huntsville, Canada. Poster.

*	**Figary, S.**, N. Detenbeck, and C. O’Donnell. May 2019. Building a spatial statistical network model of stream temperature to guide restoration decisions in an international watershed. Society for Freshwater Science. Annual meeting. Salt Lake City, Utah. Presentation.

*	**Figary, S.** and N. Detenbeck. May 2018. Intermittent and perennial stream macroinvertebrate community response to impervious cover: threshold indicator taxa analysis and permutations. Society for Freshwater Science. Annual meeting. Detroit, Michigan. Presentation. 

*	**Figary, S.** and N. Detenbeck. June 2017. Evaluating macroinvertebrate community responses to impervious cover in California with threshold indicator taxa analysis. Society for Freshwater Science. Annual meeting. Raleigh, North Carolina. Presentation. 

*	**Figary, S.** and N. Detenbeck. July 2016. Evaluating the effectiveness of best management practices and green infrastructure in the State of California. American Water Resources Association. Summer Specialty Conference: GIS and Water Resources IX. Sacramento, California. Poster. 

*	Schulz, K. L. and **S. Figary**. November 2015. Establishment and effects of predatory invasive zooplankton in the food webs of the Finger Lakes and Great Lakes. Finger Lakes Research Conference: Threats to the Finger Lakes. Geneva, New York. Presentation.

*	**Figary, S.** May 2015. A Creek in Crisis: Time for Action. Ambler, Pennsylvania. Presentation and panel discussion.

*	**Figary, S.**  March 2015. Monitoring the Delaware Watershed Initiative. Saint Joesph University Stormwater Management Workshop. Philadelphia, Pennsylvania. Presentation.

* Cooper, A, J. Musselman and **S. Figary**. March 2015. Streamkeepers from Scratch: Building a Volunteer Monitoring Program. Watershed Congress along the Schuylkill. Pottstown, Pennsylvania. Presentation.

*	**Figary, S.**, A. Cooper, R. Eisman, P. Gardener, and B. Nyholm. January 2015. Using Citizen Scientists To Monitor Watershed Improvements In Five Philadelphia Area Watersheds. Delaware Estuary Science & Environmental Summit. Cape May, New Jersey. Poster presentation.

*	**Figary, S.**,  K. L. Schulz, M. A. Teece, and L. G. Rudstam. April 2013. Why are half of New York Finger Lakes invaded by *Cercopagis pengoi*, while the other half have remained non-invaded for over a decade? Graduate Level Research Conference. Brockport, New York. Presentation.


```{r, echo=FALSE}

# *	**Figary, S.**,  K. L. Schulz, M. A. Teece, and L. G. Rudstam. 2012. Unexpected effects of an invasive zooplankton, *Cercopagis pengoi*, on the trophic position of planktivorous fish, *Alsoa pseudoharengus*, in New York’s Finger Lakes. International Association of Great Lakes Research Conference. Cornwall, Ontario, Canada. Presentation.

# *	**Figary, S.**,  K. L. Schulz, M. A. Teece, and L. G. Rudstam. 2011. Investigating the impact of an invasive zooplankton, *Cercopagis pengoi*, on the length of food chains in New York's Finger Lakes. Spotlight-on-Research. Syracuse, New York. **Award winning poster.**
# 
# * Hoover, C.,	**S. Figary,**, and K. L. Schulz.  2011. Invasive mussels in New York’s Finger Lakes: Are mussel demography, density and species composition correlated with lake nutrient concentrations? Spotlight-on-Research. Syracuse, New York. **Award winning poster.**
# 
# *	**Figary, S.**, K. L. Schulz, M. A. Teece, and L. G. Rudstam.  Investigating the impact of an invasive zooplankton, *Cercopagis pengoi*, on the length of food chains in New York's Finger Lakes. Poster.
#     + Dec 2011. Great Lakes Research Consortium. Syracuse, New York. 
#     + Feb 2011. Association of the Sciences of Limnology and Oceanography Conference. San Juan, Puerto Rico.

# *	**Figary, S.** and K. L. Schulz. 2010. Exploiting a natural experiment: Investigating the impact of an invasive zooplankton, *Cercopagis pengoi*, on the food webs of the New York Finger Lakes. Finger Lakes Institute Conference. Geneva, New York. Poster.
# 
# *	**Figary, S.** 2010. The impacts of invasive zooplankton, *Cercopagis pengoi*, on the food webs of the New York Finger Lakes. Aquabreak Seminar. Syracuse, New York.  Presentation.
# 
# *	**Figary, S.** 2008. The deep chlorophyll layer of Lake Ontario. SUNY College at Brockport Scholar’s Day. Brockport, New York. Presentation.
```







